Sketch of DP - Bayesian Inference

### 2018-07-16 main-sketch.tex
conflicts solved

  \Pr(\theta | \dataobs) = \frac{\Pr(\dataobs | \theta) \cdot \Pr(\xis)}{\Pr(\dataobs)}

@@

  \Pr(\dataobs|\vtheta)\equiv \displaystyle\prod_{a\in\datauni}\alpha_{a}^{z_a}
\todo{to check}\]
where $z_a=\displaystyle\sum_{i=1}^{n}\iverson{x_i=a}$, where in $\iverson{\cdot}$ we use

@@

  \Pr(\vtheta|\dataobs)=\todo{to type down}\dirichlet(\vtheta+...)

@@

\noindent Also, in previous works, the accuracy has been measured again with respect to
$\ell_1$ norm. That is, an upper bound has been given to
\[
  \Pr[|\alpha - \tilde\alpha| + |\beta - \tilde\beta |\geq \gamma ]
\]
where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are as  defined above.
In this work we will use a metric based on a different norm to compute the sensitivity
and provide guarantees on the accuracy. In particular we will consider a metric
over probability measures and not over the parameters that represent them.
Specifically, we will use the Hellinger distance, which for two beta distributions
$\betad(\alpha_1, \beta_1), \betad(\alpha_2, \beta_2)$ is defined as
\[
  \hellinger()\equiv\todo{to type down}
\]
The same change of metric will be applied to the experimental accuracy guarantees.
\section{Technical Problem Statement}
\label{sec_bayesInfer}
The posterior belief about parameters $\xis$ is inferred from the
group of sensitive data. Because it is usually published in form of a
distribution, for example, $\betad(\alpha',\beta'), \cdots,$ itself
can relieve a lot of information about sensitive data. So, the
sensitive information we want to protect here is the posterior belief,
i.e., $Pr(\xis | \dataobs)$, rather than just a sample drew from
it\cite{foulds2016theory}. Then it will be better if we can use a
distance over two distributions to measure the accuracy than a
distance over just parameters or values when we are protecting a
distribution, for instance, Hellinger distance in our paper. When we
measure the accuracy between true posterior and protected posterior
using Hellinger distance, it would be better we can have a protection
mechanism based on Hellinger distance. However, current mechanisms are
mainly based on $l_1$ norm by Laplace mechanism
\cite{zhang2016differential} \cite{xiao2012bayesian}. That's why we
design our exponential mechanism over Hellinger distance to protect
the whole posterior distribution.

\section{Baseline Approach - Laplace Mechanism}
\label{sec_lap}
Based on the posterior results from Bayesian inference, we calculate the Laplace mechanism updates on posterior and get the private results under Laplace mechanism. In the case of $m$ dimension Dirichlet distribution, we will add $(m-1)$ i.i.d. Laplace noises $\{| Lap_1 |, | Lap_2 |, \cdots, | Lap_{m-1} |\}$ to the output, where $Lap_i = floor(Y)$, $Y \sim Lap(\frac{2}{\epsilon})$. The private posterior then will be $\dirichlet(\alpha_1 + n_1 + | Lap_1 |, \alpha_2 + n_2 + | Lap_2 |, \cdots, \alpha_m + n - (Lap_1 + \cdots + Lap_{m-1}))$.

>>>>

  \Pr(\theta | \dataobs) = \frac{\Pr(\dataobs | \theta) \cdot \Pr(\theta)}{\Pr(\dataobs)}

@@

  \Pr(\dataobs|\vtheta)\equiv \displaystyle\prod_{a_i\in\datauni}\theta_{i}^{\Delta \alpha_i}
where $\Delta \alpha_i=\displaystyle\sum_{i=1}^{n}\iverson{x_i=a_i}$, where in $\iverson{\cdot}$ we use

@@

  \Pr(\vtheta|\dataobs)=\dirichlet(\valpha+\Delta \valpha)

@@

\noindent Also, in previous works, the accuracy has been measured again with respect to
$\ell_1$ norm. That is, an lower bound has been given to
\[
  \Pr[|\alpha - \tilde\alpha| + |\beta - \tilde\beta |\geq \gamma ]
\]
where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are as  defined above.
In this work we will use a metric based on a different norm to compute the sensitivity
and provide guarantees on the accuracy. In particular we will consider a metric
over probability measures and not over the parameters that represent them.
Specifically, we will use the Hellinger distance, which for two beta distributions
$\betad(\alpha_1, \beta_1), \betad(\alpha_2, \beta_2)$ is defined as
\[
  \hellinger()\equiv\todo{to type down}
\]
The same change of metric will be applied to the experimental accuracy guarantees.
\section{Technical Problem Statement}
\label{sec_bayesInfer}
The posterior belief about parameters $\xis$ is inferred from the
group of sensitive data. Because it is usually published in form of a
distribution, for example, $\betad(\alpha',\beta'), \cdots,$ itself
can relieve a lot of information about sensitive data. So, the
sensitive information we want to protect here is the posterior belief,
i.e., $Pr(\xis | \dataobs)$, rather than just a sample drew from
it\cite{foulds2016theory}. Then it will be better if we can use a
distance over two distributions to measure the accuracy than a
distance over just parameters or values when we are protecting a
distribution, for instance, Hellinger distance in our paper. When we
measure the accuracy between true posterior and protected posterior
using Hellinger distance, it would be better we can have a protection
mechanism based on Hellinger distance. However, current mechanisms are
mainly based on $l_1$ norm by Laplace mechanism
\cite{zhang2016differential} \cite{xiao2012bayesian}. That's why we
design our exponential mechanism over Hellinger distance to protect
the whole posterior distribution.

\section{Baseline Approach - Laplace Mechanism}
\label{sec_lap}
Our baseline approach come from the algorithm designed by \citet{zhang2016differential} that adding Laplace noise (\citet{dwork2014algorithmic}) to posterior parameters to preserve privacy. They perturbed the parameter updates of $\betad$ distribution from Bayesian inference and truncated to rule out invalid $\betad$ parameters to get the protected posteriors. Furthermore, we extend their algorithm to the case of $m$ dimensional Dirichlet distributions, where we add $(m-1)$ i.i.d. Laplace noises $\{Lap_1 , Lap_2, \cdots, Lap_{m-1} \}$ and truncate in the same way. 
%where $Lap_i = floor(Y)$, $Y \sim Lap(\frac{2}{\epsilon})$. 
The private posterior is $\dirichlet(\valpha + \Delta \valpha')$, where $\Delta \valpha'$ is the perturbed parameter updates.
